Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-10-10 manuscript2.RMD
updates

Responses to systematic resistance training (RT) vary widely between individuals, with as much as 10-15% showing impaired skeletal muscle growth in response to standardized training interventions [@alvarez_interindividual_2018; @mann_high_2014; @thalacker-mercer_cluster_2013]. While there certainly may be differences in the genetic predisposition in terms of readiness to adapt to exercise [@thalacker-mercer_cluster_2013], there are also recent studies showing that epigenetic factors such as ribosomal DNA (rDNA) availability may also impact the ability to mount an anabolic response to RT [@figueiredo_genetic_2021]. Indeed, the ability to synthesise ribosomes during a period of RT is connected to the magnitude of RT-induced responses in an individual [@hammarstrom_benefits_2020]. For instance, increasing training volume generally induces greater ribosome biogenesis and thus, greater benefits of RT [@hammarstrom_benefits_2020;@krieger_single_2009;@schoenfeld_strength_2017]. However, as evident from Hammarström et al. (2020), not all participants experienced increased muscle mass and -strength despite increasing training volume. Therefore, other means than modification of RT variables alone seem necessary to optimise individual responses to RT.

>>>>

Responses to systematic resistance training (RT) vary widely between individuals, with as much as 10-15% showing impaired skeletal muscle growth in response to standardized training interventions [@alvarez_interindividual_2018; @mann_high_2014; @thalacker-mercer_cluster_2013]. There may be differences in the genetic predisposition in terms of readiness to adapt to exercise [@thalacker-mercer_cluster_2013], however, the internal physiological milieu seem favourably shaped for muscle growth by factors such as different types of training stress and nutrients [@figueiredo_genetic_2021; @sebata_control_2018; @thalacker-mercer_cluster_2013]. Indeed, training stress and nutrients impact the ability to synthesis ribosomes, which in turn is connected to the magnitude of RT-induced responses in an individual [@hammarstrom_benefits_2020; @kusnadi_regulation_2015; @sebata_control_2018]. For instance, increasing training volume generally induces greater ribosome biogenesis and thus, greater benefits of RT [@hammarstrom_benefits_2020;@krieger_single_2009;@schoenfeld_strength_2017]. Still, as evident from Hammarström et al. (2020), not all participants experience increased muscle mass and -strength despite increasing training volume. Therefore, other means than modification of RT variables alone seem necessary to optimise individual responses to RT.
